Networked Character Devices

### 2011-12-09 report/presentation.tex
presentation: print all references, handout mode for no overlay
presentation: add udev and ncadmin frames

\documentclass[xcolor=dvipsnames]{beamer}
\usetheme{AnnArbor}
\usecolortheme{beaver}
\setbeamercovered{transparent=25}
\setbeamertemplate{blocks}[rounded][shadow=false] 
\setbeamertemplate{navigation symbols}{}

@@

\begin{frame}{\texttt{udev}}
\end{frame}

\begin{frame}{\texttt{ncadmin}}
\end{frame}

@@

%---Bibliography---%
\begin{frame}{\bf Bibliography}

\bibliography{refs}

>>>>

\documentclass[handout]{beamer}
\usetheme{AnnArbor}
\usecolortheme{beaver}
\setbeamercovered{transparent=25}
\setbeamertemplate{blocks}[rounded][shadow=false] 
\setbeamertemplate{navigation symbols}{}

@@

\begin{frame}[t,fragile]{\texttt{udev}}
  \begin{lstlisting}[gobble=4,title=no way to set permissions within kernel,language=]
    ACTION=="add", SUBSYSTEM=="netchar", MODE="0666"
  \end{lstlisting}
  \begin{lstlisting}[gobble=4,title=cannot retroactively apply input attributes,language=]
    $ udevadm info -qall -n /dev/input/event8
    P: /devices/virtual/input/input8/event8
    N: input/event8
    E: DEVNAME=/dev/input/event8
    E: DEVPATH=/devices/virtual/input/input8/event8
    E: ID_INPUT=1
    E: ID_INPUT_KEY=1
    E: SUBSYSTEM=input
  \end{lstlisting}
\end{frame}

\begin{frame}[fragile]{\texttt{ncadmin}}
  \begin{lstlisting}[gobble=4,language=]
    usage: ncadmin command [args]

      The following commands are supported:

      add server port [name]
        server - an ip address
        port   - a port
        name   - optional name relative to /dev. if no name is
                 specified /dev/netchar/import# will be used

      rm name
        name   - the device relative to /dev to remove
  \end{lstlisting}
  \begin{itemize}
    \item<2-> does nothing!
    \item<3-> could use discovery service
    \item<4-> requires individual \texttt{cdev}s
    \item<5-> name is optional
  \end{itemize}
\end{frame}

@@

%---Bibliography---%
\begin{frame}[t,allowframebreaks]{\bf Bibliography}
\nocite{*}
\bibliography{refs}
\end{frame}
